Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-18 sections/01-introduction.tex
Update on Overleaf.

The above-described trending idea is also of fundamental interest for evaluating and comparing forecasting methods. 
While measurement series are created by recording data using measuring instruments or direct observation, forecasting predicts the future based on historical data, patterns, and exogenous factors. 
The forecast is computed based on the current value of the quantity of interest and an estimate of the development until the target time.
A forecast's trending is perfectly consistent with the actual development of the target value if the actual change in the target value over this period matches the forecast change. 
In the current practice, a forecasting method is usually evaluated in terms of its prediction accuracy, measuring the deviation of the prediction from the actual outcome of the target variable; different measures are, for example, reviewed in \cite{hyndman2006another}. 
Popular measures of this type are scale-dependent measures such as the \ac{rmse} or measures based on percentage errors such as the root mean squared percentage error. 
These typical measures are based on the absolute difference between the prediction and the true values, locally or globally. 
They are not capable of assessing the trending ability discussed above.

>>>>

The above-described trending idea is also of fundamental interest for evaluating and comparing forecasting methods. 
While measurement series are created by recording data using measuring instruments or direct observation, forecasting predicts the future based on historical data, patterns, and exogenous factors. 
The forecast is computed based on the current value of the quantity of interest and an estimate of the development until the target time.
A forecast's trending is perfectly consistent with the actual development of the target value if the actual change in the target value over this period matches the forecast change. 
In the current practice, a forecasting method is usually evaluated in terms of its prediction accuracy, measuring the deviation of the prediction from the actual outcome of the target variable; different measures are, for example, reviewed in \parencite{hyndman2006another}. 
Popular measures of this type are scale-dependent measures such as the \ac{rmse} or measures based on percentage errors such as the root mean squared percentage error. 
These typical measures are based on the absolute difference between the prediction and the true values, locally or globally. 
They are not capable of assessing the trending ability discussed above.
